### 2017-07-27 ICRA-RA-L2018/theorynrobAlgs.tex
Final version of IROS is added. New paper started

\section{Position Control of $n$ Robots Using Boundary Interaction}\label{sec:PostionControlnRobots}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The ideas from Alg. \ref{alg:optimalAlg}  can be extended to control the position of $n$ particles using wall friction.
The solution is complete, but not optimal, and requires the starting and final configurations of particles to be disjoint.
The solution described here is an iterative procedure with $n$ loops. 
 The $k^{\text{th}}$ loop moves the $k^{\text{th}}$ robot from a \emph{staging zone} to the desired position in a \emph{build zone}. 
  All robots move according to the global input, but due to wall friction, at the end of the $k^{\text{th}}$ loop, robots 1 through $k$ are in their desired final configuration in the build zone, and robots $k+1$ to $n$ are in the staging zone. 
   See Fig.~\ref{fig:simulationNrobot} for a schematic of the build and staging zones.

\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{PositionNrobots.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:simulationNrobot}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, $n$ robot position control  using wall friction.
}
\end{figure}

Assume an open workspace with four axis-aligned walls with infinite friction.
The axis-aligned build zone of dimension $(w_b, h_b)$ containing the final configuration of $n$ robots must be disjoint from the axis-aligned staging zone of dimension $(w_s, h_s)$  containing the starting configuration of $n$ robots.
 Without loss of generality, assume the build zone  is above the staging zone.  Let $d$ be the diameter of the particles.
Furthermore, there must be at least $\epsilon$ space above the build zone, $\epsilon$ below the staging zone, and $\epsilon + d$ to the left of the build and staging zone.  The minimum workspace is then $(\epsilon + d + \max(w_b,w_s), 2\epsilon + h_s,h_b)$.

@@

\begin{algorithm}
\caption{PositionControl$n$RobotsUsingWallFriction($k$)}\label{alg:PosControlNRobots}
\begin{algorithmic}[1]
\State Move( $-\epsilon, d/2-p_{ky}$) % move  away from right wall and down till robot k touches bottom

@@

The hardware platform depicted in Fig.~\ref{fig:construction2d} is an assembled practical setup that assumes that $\epsilon= 1$ cm. 
The workspace is a $7\times 7$ cm grid space. 
All particles are 3D-printed plastic whose top is a 1cm diameter cylinder with a narrower base that encapsulates a steel bearing ball.
Wall friction is emulated by a toothed wall design to keep particles from moving out of place while implementing the drift move. 
The workspace boundary is mounted on top of a white sheet of cardboard.
Underneath the cardboard, a grid of 3mm diameter magnets glued with 1 cm spacing to a thin board generates the global control input.
 A video attachment  shows the algorithm at work. 
This discretized setup requires several modifications to Alg.~\ref{alg:PosControlNRobots}.
 In this demonstration, all moves are 1 cm in length.
   All drift moves are an counterclockwise \emph{square} move  of size 1 cm$\times$1 cm. 
   Once the $k^{\text{th}}$ roller gets to its designated location in each loop, a correction step is implemented. 
   This correction step increases by two the total number of moves required per particle.
   Fig.~\ref{fig:simulationNrobot} shows there are only 6 stages per particle involved in Alg.~\ref{alg:PosControlNRobots}.
The fixed step algorithm requires 8 stages per particle as shown in Fig.~\ref{fig:construction2d}.

@@

\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{multirobotSliderHardware2.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:construction2d}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, discretized $n$ robot position control  using wall friction.
}
\end{figure}

>>>>

\section{Position Control of $n$ Robots Using Boundary Interaction}\label{sec:PostionControlnRobots}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The ideas from Alg. \ref{alg:optimalAlg}  can be extended to control the position of $n$ particles using walls with non-slip contact.
The solution is complete, but not optimal, and requires the starting and final configurations of particles to be disjoint.
The solution described here is an iterative procedure with $n$ loops. 
 The $k^{\text{th}}$ loop moves the $k^{\text{th}}$ robot from a \emph{staging zone} to the desired position in a \emph{build zone}. 
  All robots move according to the uniform input, but due to non-slip wall contacts, at the end of the $k^{\text{th}}$ loop, robots 1 through $k$ are in their desired final configuration in the build zone, and robots $k+1$ to $n$ are in the staging zone. 
   See Fig.~\ref{fig:simulationNrobot} for a schematic of the build and staging zones.

\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{PositionNrobots.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:simulationNrobot}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, $n$ robot position control  using walls with non-slip contact.
}
\end{figure}

Assume an open workspace with four axis-aligned walls with non-slip contact.
The axis-aligned build zone of dimension $(w_b, h_b)$ containing the final configuration of $n$ robots must be disjoint from the axis-aligned staging zone of dimension $(w_s, h_s)$  containing the starting configuration of $n$ robots.
 Without loss of generality, assume the build zone  is above the staging zone.  Let $d$ be the diameter of the particles.
Furthermore, there must be at least $\epsilon$ space above the build zone, $\epsilon$ below the staging zone, and $\epsilon + d$ to the left of the build and staging zone.  The minimum workspace is then $(\epsilon + d + \max(w_b,w_s), 2\epsilon + h_s,h_b)$.

@@

\begin{algorithm}
\caption{PositionControl$n$Robots($k$)}\label{alg:PosControlNRobots}
\begin{algorithmic}[1]
\State Move( $-\epsilon, d/2-p_{ky}$) % move  away from right wall and down till robot k touches bottom

@@

The hardware platform depicted in Fig.~\ref{fig:construction2d} is an assembled practical setup that assumes that $\epsilon= 1$ cm. 
The workspace is a $7\times 7$ cm grid space. 
All particles are 3D-printed plastic whose top is a 1cm diameter cylinder with a narrower base that encapsulates a steel bearing ball.
Non-slip wall contact is generated by a toothed wall design to keep particles from moving out of place while implementing the drift move. 
The workspace boundary is mounted on top of a white sheet of cardboard.
Underneath the cardboard, a grid of 3mm diameter magnets glued with 1 cm spacing to a thin board generates the uniform control input.
 A video attachment  shows the algorithm at work. 
This discretized setup requires several modifications to Alg.~\ref{alg:PosControlNRobots}.
 In this demonstration, all moves are 1 cm in length.
   All drift moves are a counterclockwise \emph{square} move  of size 1 cm$\times$1 cm. 
   Once the $k^{\text{th}}$ particle gets to its designated location in each loop, a correction step is implemented. 
   This correction step increases by two the total number of moves required per particle.
   Fig.~\ref{fig:simulationNrobot} shows there are only 6 stages per particle involved in Alg.~\ref{alg:PosControlNRobots}.
The fixed step algorithm requires 8 stages per particle as shown in Fig.~\ref{fig:construction2d}.

@@

\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{multirobotSliderHardware2.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:construction2d}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, discretized $n$ robot position control  using walls that enforce non-slip contact.
}
\end{figure}

### 2017-07-27 JournalTorqueControl/theory.tex
Some of Dylan's comments are affected
Edited some texts
Final version of IROS is added. New paper started

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{Uniform.pdf}%\put(1,55){a)}
\end{overpic}
\begin{overpic}[width =\figwid]{Triangular.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{Normal.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:PDF} Three different distributions are examined in this work: uniform, triangular, and normal.
%\vspace{-2em}
}
\end{figure*}

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{TorqueUni.pdf}%\put(1,55){a)}
\end{overpic}
\begin{overpic}[width =\figwid]{TorqueTri.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{TorqueNormal.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:torque} Torque with regard to mean position, $\mu$. Mean position is the pushing location.
%\vspace{-2em}
}
\end{figure*}

First,  $l$ and $u$ for simplicity of the following derivations are defined for the uniform distribution. 
%defining torque uniform distribution
\begin{align}
l &= \max(0,\mu -\sqrt{3} \sigma) \, , u = \min({1,\mu+\sqrt{3}\sigma})
\end{align}
Therefore, the torque applied is:
\begin{align}
\tau_u &=  \frac{u^2-l^2}{4\sqrt{3}\sigma} \textrm{  for    }  u>l
\end{align}
To simplify derivations for triangular distribution we define bounds of integration as:
%define torque for triangular:
\begin{align}
l_1 &= \max({0,\mu-\sqrt{6}\sigma})\, , l_2 = \max({0,\mu})\\ \nonumber
u_1 &= \min({1,\mu})\, , u_2 = \min({1,\mu+\sqrt{6}\sigma}) \nonumber
\end{align}
Thus, torque is:
\begin{align}
\tau_t &= \frac{\tau_{left} + \tau_{right}}{36\sigma^2}
\end{align}
where $\tau_{left}$ and $\tau_{right}$ are defined as:
\begin{align}
\tau_{left} &=  {u_1}^2(2u_1 - 3\mu+3\sqrt{6}\sigma)\\ \nonumber
&-2{l_1}^3+3{l_1}^2(\mu-\sqrt{6}\sigma), & \textrm{for     } u_1 > l_1\\ \nonumber
\tau_{right} &= 2{l_2}^3-3{l_2}^2(\mu+\sqrt{6}\sigma)\\ \nonumber
&-{u_2}^2(2u_2 - 3\mu-3\sqrt{6}\sigma),  & \textrm{for     } u_2 > l_2\\ \nonumber
\end{align}
Torque by a uniformly distributed swarm is defined by:
%defining torque normal distribution
\begin{align} \label{eq:normalTorque}
\tau_n &= \frac{\left(e^{\frac{\mu^2}{2\sigma^2}}-e^{\frac{(1-\mu)^2}{2\sigma^2}}\right)\sigma}{\sqrt{2\pi}}+ \frac{\mu}{2}\left(\erf\left(\frac{1-\mu}{\sqrt{2}\sigma}\right)+\erf\left(\frac{\mu}{\sqrt{2}\sigma}\right)\right) 
\end{align}

@@

\subsection{Free object torque}
In this problem, the torque applied to a free rod of length 2 from $[-1,0]$ to $[1,0]$, is:
\begin{equation}
\tau_{free} = \int_{-1}^1 x\,p(x)\, dx
\end{equation}
For calculating free object torque for a uniformly distributed swarm, $l_f$ and $u_f$ are defined for simplicity of derivations. 
%torque uniform free
\begin{align}
l_f &= \max({-1,\mu -\sqrt{3} \sigma}),\, u_f = \min({1,\mu+\sqrt{3}\sigma})
\end{align}

@@

%torque triangular free
To simplify derivations for a triangularly distributed swarm, we define bounds of integration as:
\begin{align}
l_{f1} &= \max({-1,\mu-\sqrt{6}\sigma}), \,l_{f2} = \max({-1,\mu})\\ \nonumber
u_{f1} &= \min({1,\mu}), \, u_{f2} = \min({1,\mu+\sqrt{6}\sigma}) \nonumber
\end{align}
Torque is:
\begin{align}
\tau_{tf} = \frac{\tau_{fleft}+ \tau_{fright}}{36\sigma^2}
\end{align}
where $\tau_{fleft}$ and $\tau_{fright}$ is defined as
\begin{align}\nonumber
\tau_{fleft} &=  {u_{f1}}^2(2u_{f1} - 3\mu+3\sqrt{6}\sigma)\\ \nonumber
&-2{l_{f1}}^3+3{l_{f1}}^2(\mu-\sqrt{6}\sigma) &   \textrm{for     } u_{f1} > l_{f1}\\ \nonumber
\tau_{fright} &= 2{l_{f2}}^3-3{l_{f2}}^2(\mu+\sqrt{6}\sigma)\\ \nonumber
&+{u_{f2}}^2( 3\mu-2u_{f2}+3\sqrt{6}\sigma) &   \textrm{for     } u_{f2} > l_{f2}\\ \nonumber
\end{align}

>>>>

%\begin{figure*}
%\centering
%\renewcommand{\figwid}{0.66\columnwidth}
%\begin{overpic}[width =\figwid]{Uniform.pdf}%\put(1,55){a)}
%\end{overpic}
%\begin{overpic}[width =\figwid]{Triangular.pdf}
%\end{overpic}
%\begin{overpic}[width =\figwid]{Normal.pdf}
%\end{overpic}
%\vspace{-0.5em}
%\caption{\label{fig:PDF} Three different distributions are examined in this work: uniform, triangular, and normal.
%%\vspace{-2em}
%}
%\end{figure*}

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{TorqueUni.pdf}%\put(1,55){a)}
\end{overpic}
\begin{overpic}[width =\figwid]{TorqueTri.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{TorqueNormal.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:torque} Torque with regard to mean position, $\mu$. Mean position is the pushing location along a rod extending from 0 to 1.
%\vspace{-2em}
}
\end{figure*}

First,  $l$ and $u$ for simplicity of the following derivations are defined for the uniform distribution. 
%defining torque uniform distribution
\begin{align}
l &= \max(0,\mu -\sqrt{3} \sigma) \, , u = \min({1,\mu+\sqrt{3}\sigma})
\end{align}
Therefore, the torque applied is:
\begin{align}
\tau_u &=  \frac{u^2-l^2}{4\sqrt{3}\sigma} \textrm{  for    }  u>l
\end{align}
To simplify derivations for triangular distribution we define bounds of integration as:
%define torque for triangular:
\begin{align}
l_1 &= \max({0,\mu-\sqrt{6}\sigma})\, , l_2 = \max({0,\mu})\\ \nonumber
u_1 &= \min({1,\mu})\, , u_2 = \min({1,\mu+\sqrt{6}\sigma}) \nonumber
\end{align}
Thus, torque is:
\begin{align}
\tau_t &= \frac{\tau_{left} + \tau_{right}}{36\sigma^2}
\end{align}
where $\tau_{left}$ and $\tau_{right}$ are defined as:
\begin{align}
\tau_{l} &=  {u_1}^2(2u_1 - 3\mu+3\sqrt{6}\sigma)\\ \nonumber
&-2{l_1}^3+3{l_1}^2(\mu-\sqrt{6}\sigma), & \textrm{for     } u_1 > l_1\\ \nonumber
\tau_{r} &= 2{l_2}^3-3{l_2}^2(\mu+\sqrt{6}\sigma)\\ \nonumber
&-{u_2}^2(2u_2 - 3\mu-3\sqrt{6}\sigma),  & \textrm{for     } u_2 > l_2\\ \nonumber
\end{align}
Torque by a uniformly distributed swarm is defined by:
%defining torque normal distribution
\begin{align} \label{eq:normalTorque}
\tau_n &= \frac{\left(e^{\frac{\mu^2}{2\sigma^2}}-e^{\frac{(1-\mu)^2}{2\sigma^2}}\right)\sigma}{\sqrt{2\pi}}\\ \nonumber
&+ \frac{\mu}{2}\left(\erf\left(\frac{1-\mu}{\sqrt{2}\sigma}\right)+\erf\left(\frac{\mu}{\sqrt{2}\sigma}\right)\right) 
\end{align}

@@

\subsection{Free object torque}
In this problem, the torque applied to a free rod of length 2 from $[-1,0]$ to $[1,0]$, is:
\begin{equation}
\tau_{f} = \int_{-1}^1 x\,p(x)\, dx
\end{equation}
For calculating free object torque for a uniformly distributed swarm, $l_f$ and $u_f$ are defined for simplicity of derivations. 
%torque uniform free
\begin{align}
l_f &= \max({-1,\mu -\sqrt{3} \sigma}),\, u_f = \min({1,\mu+\sqrt{3}\sigma})
\end{align}

@@

%torque triangular free
To simplify derivations for a triangularly distributed swarm, we define bounds of integration as:
\begin{align}
l_{f1} &= \max({-1,\mu-\sqrt{6}\sigma}), \,l_{f2} = \max({-1,\mu})\\ \nonumber
u_{f1} &= \min({1,\mu}), \, u_{f2} = \min({1,\mu+\sqrt{6}\sigma}) \nonumber
\end{align}
Torque is:
\begin{align}
\tau_{tf} = \frac{\tau_{fl}+ \tau_{fr}}{36\sigma^2}
\end{align}
where $\tau_{fl}$ and $\tau_{fr}$ is defined as
\begin{align}\nonumber
\tau_{fl} &=  {u_{f1}}^2(2u_{f1} - 3\mu+3\sqrt{6}\sigma)\\ \nonumber
&-2{l_{f1}}^3+3{l_{f1}}^2(\mu-\sqrt{6}\sigma) &   \textrm{for     } u_{f1} > l_{f1}\\ \nonumber
\tau_{fr} &= 2{l_{f2}}^3-3{l_{f2}}^2(\mu+\sqrt{6}\sigma)\\ \nonumber
&+{u_{f2}}^2( 3\mu-2u_{f2}+3\sqrt{6}\sigma) &   \textrm{for     } u_{f2} > l_{f2}\\ \nonumber
\end{align}
